\documentclass[a4paper, 11pt]{article}
\usepackage{comment} % enables the use of multi-line comments (\ifx \fi) 
\usepackage{fullpage} % changes the margin
\usepackage[margin=35pt]{geometry}
\usepackage{graphicx}
\usepackage{microtype} 
\usepackage{titlesec}
\usepackage{color, colortbl}
\usepackage[table]{xcolor} 
\usepackage[numbers,super]{natbib}
\usepackage{bibentry}
\nobibliography*

%\usepackage[most]{tcolorbox}

%\usepackage{fontspec}
%\setmainfont{Georgia} 
\titleformat*{\section}{\large\bfseries}

\begin{document}

\noindent
\large\textbf{Committee Meeting Report} \hfill \textbf{Sahar Mozaffari} \\
\normalsize  \hfill Professor: Carole Ober  \\
GGSB Matriculated 2013 \hfill Date: 3/8/18 \\
\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}

\large\textbf{\\Progress since last Committee Meeting - October 2, 2017}
\subsection*{Awards}
% Horizontal line after name; adjust line thickness by changing the '1pt'
\begin{itemize}
    \item ASHG Reviewer's Choice Abstract Award  \hfill 2016 \& 2017
    \item Awarded \& Renewed F31 Ruth L. Kirschstein NRSA \hfill 9/2016-9/2018
    \item FASEB MARC Travel Award to ASHG \hfill 2014 \& 2015 
    \item Genetics and Regulation Training Grant \hfill 2013-2016
\end{itemize} 

\subsection*{Manuscripts in progress}
\begin{itemize}
    \item Submitting: \bibentry{Mozaffari:loXwTR9q}
    \item Revising: \bibentry{Mozaffari:dg}
    \item Submitted: \bibentry{Shiquan:G-C-HqrA}
\end{itemize}

\subsection*{Published}
\begin{itemize}
    \item \bibentry{Hart:2018cv}
    \item \bibentry{Igartua:2017ir}
    \item \bibentry{Gamazon:2015fa}
\end{itemize}

\subsection*{Oral Presentations}
\begin{itemize}
	\item GGSB Work in Progress \hfill April 2016 \& March 2017\\ \emph{Parent of Origin Effects in the Hutterites}
	\item Genetics of Model Organisms Club \hfill April 21, 2016\\  \emph{Parent of Origin Effects in the Hutterites}
  	\item Human Genetics Work in Progress \hfill January 20, 2016\\ \emph{Parent of Origin Effects} 
	\item Molecular Biosciences Retreat \hfill November 5, 2015\\ Mozaffari SV, DeCara J, Shah S, Herman C, Lang R, Nicolae D, Ober C., \emph{Parent of Origin GWAS with Cardiovascular Disease Associated Traits in the Hutterites.} 2015: Nov 5; Galena, IL.
    \item ASHG\hfill October 9, 2015\\ Mozaffari SV, DeCara J, Shah S, Herman C, Lang R, Nicolae D, Ober C., \emph{Parent of Origin GWAS of CVD-Associated Phenotypes in the Hutterites} (Abstract Program \#310). Presented at the Annual Meeting of The American Society of Human Genetics; 2015: Oct 9; Baltimore, MD. 
  

\end{itemize}

\subsection*{Posters}
\begin{itemize}
    \item Reviewer's Choice Abstract Award: \\Mozaffari SV, Nicolae D, Ober C. Identifying Imprinted Genes and Parent of Origin Effects on Gene Expression in the Hutterites. Poster presented at the Annual Meeting of The American Society of Human Genetics Conference; 2017: Oct 17-21; Orlando, FL
    \item Mozaffari SV, Nicolae D, Ober C. \emph{Opposite Allele Parent of Origin Effects on Cardiovascular and Asthma Associated Traits in the Hutterites}. Poster presented at the Gordon Research Seminar and Conference; 2017: July 8-14; Stowe, VT
    \item Reviewer's Choice Abstract Award: \\Mozaffari SV, Nicolae D, Ober C. Opposite Allele Parent of Origin Effects on Body Mass Index in the Hutterites. Poster presented at the Annual Meeting of The American Society of Human Genetics Conference; 2016: Oct 18-22; Vancouver, Canada
    \item Mozaffari SV, Gamazon E, Aquino-Michaels K, Cox NJ, Im HK. \emph{Quantifying Context Specificity of Gene Regulation using Predicted Gene Expression Levels.} Poster presented at the Annual Meeting of The American Society of Human Genetics Conference; 2014: Oct 18-22; San Diego, CA 

\end{itemize}

\subsection*{Teaching Assistantship Requirements Completed}
\begin{itemize}
	\item BIOS 20187 \emph{Fundamentals of Genetics} \hfill Winter 2018\\
		- Undergraduate Course: Recent developments in molecular genetics and the human genome project integrated into the structure of classical genetics.
	\item HGEN 47000 \emph{Human Genetics} \hfill Fall 2015 \& 2017\\
- Graduate Course: Classic and modern approaches to studying cytogenetic, Mendelian, and complex human diseases. Grant proposal writing course. \\ - Fall 2017: Conducting two-day computational workshop on GWAS
    \item MGCB 31400 (BIOS 21236) \emph{Genetic Analysis of Model Organisms}\hfill Fall 2014\\
- Graduate \& Undergraduate Course: Introduction to genetic tools, experiments, and model organisms 
\end{itemize}



\subsection*{Additional Courses}
\begin{itemize}
    \item STAT 24500 \emph{Statistical Theory \& Methods II }\hfill Winter 2015
    \item HGEN 46900 \emph{Human Variation \& Disease} \hfill Spring 2015
    \item STAT 35500 \emph{Statistical Genetics} \hfill Spring 2015
    \item myChoice Mini-Course: \emph{Effective Writing in the Biological Sciences} \hfill Fall 2015
    \item HGEN 48600 \emph{Fundamentals of Computational Biology: Models \& Inference} \hfill Winter 2016
    \item PBHS 31831 \emph{Genetic \& Molecular Epidemiology} \hfill Spring 2016
  
	
\end{itemize}

\subsection*{Additional Workshops \& Conferences}
\begin{itemize}
	\item ComSciCon Chicago (Communicating Science Conference \& Workshop)  \hfill August 2017
	\item Gordon Research Seminar \& Conference: Human Genetics \& Genomics \hfill July 2017 \\ Discussion Leader for mentorship session at GRS
     \item Summer Institute in Statistical Genetics at the University of Washington \hfill July 2016
        \item Master R Developer Workshop taught by Hadley Wickham \hfill May 2015
\end{itemize}

\subsection*{Extracurricular}
\begin{itemize}
	\item Museum of Science \& Industry: Science Connections volunteer \hfill Fall 2014-current \\
		Introduce genetic concepts to guests in a fun and engaging way, incorporating hands-on activities.\\Assist in the Fabrication Lab helping guests design and print custom objects using 3D printers and laser cutters.

	\item myCHOICE Data Science Trek to San Francisco Bay Area \hfill November 2017 \\
		Visit PhD alumns at 23andMe, Genentech, Ancestry, Illumina, Genomic Health, etc.
		\item UChicago Software Carpentry Helper \hfill Fall 2015, 2016, \& 2017
	\item Expanding Your Horizons (EYH) Chicago: volunteer \hfill March 2017 \\
	Engage, inspire, and empower young girls to pursue STEM careers at a one-day STEM symposium where 300 middle school girls participate in hands-on science, technology, engineering and math led by academic and professional women.
   	\item myCHOICE Internship: Institute of Translational Medicine: writer \hfill Summer 2015\\Translate complex research into dynamic science stories. Share translational research stories in weekly newsletter, ITM website, and social media platforms

\end{itemize}



%\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}

%\section*{Attachments}
%Make sure to change these
%Lab Notes, HelloWorld.ic, FooBar.ic
%\fi %comment me out
\newpage

%\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
\section*{Since my last committee meeting:} %\begin{tcolorbox}[colback=white,colframe=red!75!black]
\textbf{AIM 1} To identify and characterize parent of origin effects on quantitative traits in the Hutterites. \\

	Completed with preprint on bioRxiv \cite{Mozaffari:dg}, working on revising and resubmitting. We are working on replicating the significant opposite effects of SNPs.
	
 \textbf{\\AIM 2a} To identify and characterize parent of origin effects on gene expression in 306 Hutterites.\\
 
 	Manuscript draft on imprinted genes identified in LCLs completed. Includes replication of genes in whole blood gene expression and whole blood methylation. 
 
 \textbf{\\AIM 2b} To identify and characterize parent of origin and allele specific effects on gene expression in 306 Hutterites.\\ 
 	
	I first performed opposite effect POeQTLs (similar method as in Aim 1) on total LCL gene expression. We subsetted on SNPs with at least three individuals in at least three genotype groups (out of four if you call parent of origin) and found no significant associations (Bonferonni p-value cutoff 1e-07).\\
	
	I then tested maternally inherited SNPs with the maternal gene expression and paternally inherited SNPs with paternal expression in \textit{cis}. I'll share results at the meeting. \\
	


%\end{tcolorbox}
\bibliography{report2018}
\bibliographystyle{apalike}

%\begin{thebibliography}{9}
%\bibitem{Gamazon} Gamazon, E. R., Wheeler, H. E., Shah, K. P., Mozaffari, S. V., Aquino-Michaels, K., Carroll, R. J., et al. (2015). A gene-based association method for mapping traits using reference transcriptome data. Nature Genetics, 47(9), 1091–1098. http://doi.org/10.1038/ng.3367
%\bibitem{Cusanovich} Cusanovich, D. A., Caliskan, M., Billstrand, C., Michelini, K., Chavarria, C., De Leon, S., et al. (2016). Integrated analyses of gene expression and genetic association studies in a founder population. Human Molecular Genetics, ddw061. http://doi.org/10.1093/hmg/ddw061
%\bibitem{Dobin} Dobin, A., \& Gingeras, T. R. (2015). Mapping RNA-seq Reads with STAR. Current Protocols in Bioinformatics. 51, 11.14.1–19. http://doi.org/10.1002/0471250953.bi1114s51
%\bibitem{Jun} G. Jun, M. Flickinger, K. N. Hetrick, Kurt, J. M. Romm, K. F. Doheny, G. Abecasis, M. Boehnke,and H. M. Kang, (2012) Detecting and Estimating Contamination of Human DNA Samples in Sequencing and Array-Based Genotype Data, AJHG doi:10.1016/j.ajhg.2012.09.004 (volume 91 issue 5 pp.839 - 848)
%\bibitem{van de Geijn}van de Geijn B, McVicker G, Gilad Y, Pritchard JK. (2015) WASP: allele-specific software for robust molecular quantitative trait locus discovery. Nat Meth. 12:1061-1063. doi:10.1038/nmeth.3582.
%\end{thebibliography}

\end{document}
